### 2016-09-26 projects_that_depend_on_sympy.tex
Fix Octave stuff

\href{http://octave.sourceforge.net/symbolic}{\textbf{Octave Symbolic}}~\cite{OctSymPy} &  &
  The OctSymPy package adds symbolic calculation features
  to GNU Octave. These include common CAS tools such
  as algebraic operations, calculus, equation solving, Fourier and
  Laplace transforms, variable precision arithmetic, and other features. \\

>>>>

\href{https://github.com/cbm755/octsympy}{\textbf{GNU Octave Symbolic Package}}~\cite{OctSymPy} &  &
  The OctSymPy package adds symbolic calculation features
  to GNU Octave. These include common CAS tools such
  as algebraic operations, calculus, equation solving, Fourier and
  Laplace transforms, variable precision arithmetic, and other features. \\
